DOM Review Summary

### 2024-03-18 Analysis/ReviewSummary/ReviewSummary.qmd
Study duration plot
log-scaled histogram of study duration

---
title: "DOM Review Summary"
author: "Saoirse Kelleher"
date: "March 13 2024"
date-modifed: today
abstract: "A summary of results from the DOM Review, for use in interpreting outputs and writing the review manuscript. "
abstract-title: "Summary"
format: 
  html:
    theme: minty
    toc: true
embed-resources: true
---

@@

>>>>

---
title: "DOM Review Summary"
author: "Saoirse Kelleher"
date: today
abstract: "A summary of results from the DOM Review, for use in interpreting outputs and writing the review manuscript. "
abstract-title: "Summary"
format: 
  html:
    theme: minty
    toc: true
embed-resources: true
---

@@

Study duration, defined as the length of time between the first and last survey, ranged from **`{r} min(dataCollection_clean$Duration)`** month to **`{r} max(dataCollection_clean$Duration)/12`** years.

```{r DataCollection_duration}
#| echo: false

dataCollection_clean |>
  ggplot() +
  geom_histogram(aes(x = Duration), 
                 binwidth = 0.1, fill = "darkslategrey") +
  scale_x_continuous(transform = "log10", 
                     breaks = c(1, 12, 60, 
                                120, 240, 480), 
                     labels = c("1 month", "1 year", "5 years", 
                                "10 years", "20 years", "40 years")) +
  labs(title = "Study duration distribution",
       subtitle = "Defined as time between first and last survey",
       y = "Frequency", x = "Study duration (log10 scale)")
```
